---
fontsize: 10pt
urlcolor: blue
geometry: margin=0.5in
header-includes: \renewcommand{\labelitemi}{} \usepackage[scaled]{helvet} \renewcommand\familydefault{\sfdefault} \usepackage[T1]{fontenc}
output:
  pdf_document:
    highlight: tango
    keep_tex: no
    number_sections: no
    toc: no
    toc_depth: 2
params:
  course_info: PSYC 3250 Psychological Measurement Section 01
  instructor: David Stanley
  chair: Ian Newby-Clark
  student_name: John Doe
  student_email: jdoe@uoguelph.ca
  offense: unauthorizedcooperation
  student_number: 0000000
  due_date: 0000-01-01
  submit_date: 0000-01-01
  instructor_date: today
  forward_date: today
  prelim_grade: -99
  assignment_weight: -99
  assignment_name: Assignmentname
  other_students: temp
  other_assignments: temp
  notes: temp
---
<!-- set code block background color -->
\definecolor{shadecolor}{RGB}{227, 227, 247}

```{r setup, include = FALSE}
forward_date = params$forward_date
instructor_date = params$instructor_date

offense <- params$offense

degree = "__________"
major = "__________"
semester_level = "__________"
chair_date = "_____________"


is_offense <- function(cur_offense) {
  status = cur_offense %in% offense
  if (status == TRUE) {
    output = "$\\textbf{\\boxed{\\checkmark}}$"
  } else {
    output = "$\\square$"
    output = sprintf("\\CheckBox[name = %s,width=4mm, height = 4mm, bordercolor={0 0 0}]{}", cur_offense)
  }
  return(output)
}


```

```{r, echo = FALSE, eval = TRUE, out.width="100%"} 
header_path <- system.file("image","header_image.png", package = "misconduct")
knitr::include_graphics(header_path)
```

# A. Record Information

\normalsize

**Student Name:** `r params$student_name` \hspace{5mm} **ID:** `r params$student_number`  \hspace{5mm} **Degree Program:** `r degree`

**Major:** `r major` \hspace{5mm} **Student email:** `r params$student_email` 

**Course number, Section, Title:** `r params$course_info` 

**Coordinator or Instructor's Name:** `r params$instructor` 


# B. Details of alleged Offence

\small


For more information on offences, consult the Undergraduate Calendar, Section VIII, Academic Misconduct: http://www.uoguelph.ca/registrar/calendars/undergraduate/current/ Click on Section VIII. “Undergraduate Degree Regulations and Procedures.” Then click on the section “Academic Misconduct.” If the case involves a graduate student, consult the Graduate Calendar, Section II, Academic Misconduct: http://www.uoguelph.ca/registrar/ calendars/graduate/current/ Click on Section III. “General Regulations.” Then click on the section “Academic Misconduct.”

Please select as many options that may apply. If you are unsure of the exact offence, indicate “Uncertain.”

\large

1. **Misappropriation of Other's Work:**

- `r is_offense("plagiarism")` **Plagiarism**
  - \small Misrepresenting someone else’s ideas or work as their own \large

- `r is_offense("copying")` **Copying**
  - \small Copying in whole or in part exam answers, lab reports etc. \large

- `r is_offense("unauthorizedcooperation")` **Unauthorized cooperation or collaboration**
  - \small Collaboration on any assignment which has been explicitly designated as an individual effort \large


2. **Misrepresentation and Fraud**

- `r is_offense("impersonation")` **Impersonation**
    - \small Impersonating or allowing someone to impersonate, in person or electronically, in any type of academic requirement \large
- `r is_offense("falsification")` **Falsification**
    - \small Providing a false or fraudulent document or testament for any academic purpose. Includes misrepresenting how much work an individual has contributed to a group assignment\large
- `r is_offense("withholding")` **Withholding**
    - \small Withholding records, transcripts and other academic records in order to gain unfair academic advantage \large
- `r is_offense("unauthorizedaids")` **Unauthorized aids or assistance**
    - \small Use or possession of any aid or assistance which is not specifically allowed by the Instructor or Invigilator \large


\
\

3. **Improper Access and Obstruction**
- `r is_offense("preventing access")` **Preventing access to materials**
    - \small Hiding, destroying or otherwise restricting access to any material intended for general academic use \large
- `r is_offense("obstruction")` **Obstruction and Interference**
    - \small Obstructing or interfering with the scholarly activities of others specifically to gain unfair academic advantage \large
- `r is_offense("improper access")` **Improper access**
    - \small Unlawfully accessing any confidential document or material to gain an unfair academic advantage \large
- `r is_offense("improper dissemination")` **Improper dissemination**
    - \small Unlawfully making any confidential material available to a third party \large

\vspace{2mm}

4. **Aiding and Abetting**
- `r is_offense("aiding and abetting")` **Aiding and abetting**
    - \small Knowingly aiding or abetting anyone in committing any form of academic misconduct \large

\vspace{2mm}


5. **Uncertain**
- `r is_offense("uncertain")`  \small Circumstances do not fit neatly into any one category \large

## Assignment Details: `r params$assignment_name`

**Assignment or Exam Worth What % of Final Grade:** `r params$assignment_weight`  

**Preliminary Grade:** `r params$prelim_grade`

**Assignment Due Date or Exam Date:** `r params$due_date` 
 
**Date Assignment Submitted:** `r params$submit_date`

## Grades in Other Assignments:

```{r gradetable,echo=FALSE}
knitr::kable(params$other_assignments)
```


## Names of other students, if any, associated with the students allegation:

`r params$other_students`

\pagebreak

# C. Details of Notification/Interviewing of Student Regarding Allegation

## Student Interviewed by:

**Instructor:**  `r params$instructor`  \hspace{5mm}  Yes \LARGE  $\boxed{\checkmark}$ \large \CheckBox[name=iNo, width=12pt, bordercolor={0 0 0}]{No} \hspace{5mm} **Date:** `r sprintf("%s", instructor_date)`

**Chair/Director:** `r params$chair`  \hspace{5mm}  \CheckBox[name=cYes, width=12pt, bordercolor={0 0 0}]{Yes} \hspace{2mm} \CheckBox[name=cNo, width=12pt, bordercolor={0 0 0}]{No} \hspace{5mm}    **Date:** \TextField[width=10em, bordercolor={0 0 0}]{}

**Other:** \TextField[width=10em, bordercolor={0 0 0}]{} \hspace{5mm}  \CheckBox[name=oYes, width=12pt, bordercolor={0 0 0}]{Yes} \hspace{2mm} \CheckBox[name=oNo, width=12pt, bordercolor={0 0 0}]{No} \hspace{5mm}            **Date:** \TextField[width=10em, bordercolor={0 0 0}]{}

**Date Forwarded to Chair/Director:** `r sprintf("%s", forward_date)`

**Instructor and/or Source of Allegation:** Please provide details of the alleged misconduct and your evidence-gathering activities and relevant dates (attach additional pages and documentation as necessary):

\vspace{5mm}

`r params$notes` 

\vspace{10mm}


# D. Please attach to or otherwise indicate inclusion of the following documentation (as applicable) on this form:


\CheckBox[name=optionA, width=12pt, bordercolor={0 0 0}]{} Course Outline

\CheckBox[name=optionB, width=12pt, bordercolor={0 0 0}]{} Assignment or examination instructions (indicate value of assignment/exam)

\CheckBox[name=optionC, width=12pt, bordercolor={0 0 0}]{} A preliminary grade for the assignment or test avoiding any reductions associated with possible misconduct

\CheckBox[name=optionD, width=12pt, bordercolor={0 0 0}]{} A copy of the student's work with suspicious areas highlighted or otherwise clearly noted

\CheckBox[name=optionE, width=12pt, bordercolor={0 0 0}]{} Information about the student's performance on other assignments in the course (see appropriate space given above)

\CheckBox[name=optionF, width=12pt, bordercolor={0 0 0}]{} E-mail or other correspondence related to the case

\CheckBox[name=optionG, width=12pt, bordercolor={0 0 0}]{} Names of witness(es) and/or witness statements, as appropriate

\CheckBox[name=optionH, width=12pt, bordercolor={0 0 0}]{} Any additional information that may be relevant to the allegation (please list): 

\TextField[width=17.2cm, height = 3cm, bordercolor={0 0 0}]{}


\pagebreak

# E. Signature

\TextField[width=18em,  height = 12mm, bordercolor={0 0 0}]{\textbf{Instructor Signature:}} \hspace{5mm} **Date:** \TextField[width=10em, bordercolor={0 0 0}]{}

# To be completed by Chair/Director:

**Date Received by Chair/Director:** \TextField[width=10em, bordercolor={0 0 0}]{}

**Additional Comments (attach separate sheets if necessary)**

\TextField[width=17.2cm, height = 8cm, bordercolor={0 0 0}]{}

**Date Forwarded to Associate Dean:**  \TextField[width=10em, bordercolor={0 0 0}]{}

\vspace{5mm}

\TextField[width=15em, height = 12mm, bordercolor={0 0 0}]{\textbf{Chair/Director's Signature:}} \hspace{5mm} **Date:** \TextField[width=10em, bordercolor={0 0 0}]{}

